The \dealii Library, Version 9.6

### 2024-08-12 9.6/paper.tex
Add affiliation of Jan Philipp Thiele

\hypersetup{
  pdfauthor={
    Daniel Arndt,
    Wolfgang Bangerth,
    Bruno Blais,
    Marc Fehling,
    Rene Gassm"{o}ller,
    Timo Heister,
    Luca Heltai,
    Martin Kronbichler,
    Matthias Maier,
    Peter Munch,
    Bruno Turcksin,
    David Wells
  },
  pdftitle={The deal.II Library, Version 9.6, 2024},
}

@@

\author[12]{Bruno~Turcksin}

\author[13]{David Wells}
\affil[13]{Department of Mathematics, University of North Carolina,
  Chapel Hill, NC 27516, USA.
  {\texttt{drwells@email.unc.edu}}}

>>>>

\hypersetup{
  pdfauthor={
    Daniel Arndt,
    Wolfgang Bangerth,
    Bruno Blais,
    Marc Fehling,
    Rene Gassm"{o}ller,
    Timo Heister,
    Luca Heltai,
    Martin Kronbichler,
    Matthias Maier,
    Peter Munch,
    Jan Philipp Thiele,
    Bruno Turcksin,
    David Wells
  },
  pdftitle={The deal.II Library, Version 9.6, 2024},
}

@@

\author[12]{Jan Philipp Thiele}
 \affil[12]{Weierstrass Institute for Applied Analysis and Stochastics,\newline
 Leibniz Institute in Forschungsverbund Berlin e.V.
  {\texttt{thiele@wias-berlin.de}}}

\author[13]{Bruno~Turcksin}

\author[14]{David Wells}
\affil[14]{Department of Mathematics, University of North Carolina,
  Chapel Hill, NC 27516, USA.
  {\texttt{drwells@email.unc.edu}}}
